### 2024-07-09 Scripts/Manuscript/manuscript.Rmd
made inline code more consistent, removed the data structure plot data, clarified source script functions, added Orcid IDs, and added the basic structure for funding information.

author: 
  - name          : "Goos, C."
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Professor Cobbenhagenlaan 125, 5037 DB, Tilburg, The Netherlands"
    email         : "c.goos@tilburguniversity.edu"
    role: # Contributorship roles (e.g., CRediT, https://credit.niso.org/)
      - "Conceptualization"
      - "Data curation"
      - "Formal Analysis"
      - "Investigation"
      - "Methodology"
      - "Project Administration"
      - "Software"
      - "Visualization"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"
  - name          : "Bakker, M."
    affiliation   : "1"
    role:
      - "Supervision"
      - "Writing - Review & Editing"
  - name          : "Wicherts, J.M."
    affiliation   : "1"
    role:
      - "Supervision"
      - "Writing - Review & Editing"
  - name          : "Nuijten, M.B."
    affiliation   : "1"
    role:
      - "Conceptualization"
      - "Project Administration"
      - "Supervision"
      - "Validation"
      - "Writing - Review & Editing"

@@

To be included in the planned analyses on calculated reliabilities, the measure had to be a scale consisting of multiple items. If cleaned data was available this was chosen over raw data, to ensure that variables were coded as intended (e.g. no reverse-coded items). Pilot data were omitted from the analyses entirely. These criteria resulted in suitable item score data from `r apa_num(length(unique(data_h3_multiple$g)))` replication sets spread across on average approximately `r apa_num(mean(table(data_h3_multiple$g)), digits = 0)` lab locations for the analyses of Hypotheses 2 & 3.

@@

## graphs
# plot for data visualization overview
plot_data_structure_data <- data_prep_data_structure_plot(data_h4)
# plot accompanying the results for Hypotheses 4, 5, & 6.
plot_456_data <- data_prep_plot_456(data_h6)
# plot accompanying the results for Hypotheses 4, & 6
plot_46_data <- data_prep_plot_46(data_h6[c(3, 6, 9, 12, 15, 18, 36, 39, 42, 45, 48, 51)])
plot_46_data_rev <- data_prep_plot_46(data_h6[c(3, 21, 24, 27, 30, 33, 36, 54, 57, 60, 63, 66)])
# plot accompanying the results for Hypotheses 2, & 3
plot_23_data_alpha <- data_prep_plot_23_alpha(data_h3_multiple)
plot_23_data_omega <- data_prep_plot_23_omega(data_h3_multiple)
plot_23_data_reported_alpha <- data_prep_plot_23_alpha_reported(coded_data_original_shortened, data_h3_avg, data_h3_multiple)

@@

open_data(data = plot_data_structure_data, filename = paste0(paste0(
  "Data/AnalysisData/", deparse(substitute(plot_data_structure_data))), ".csv"),
  codebook = paste0(paste0(
    "Data/AnalysisData/codebook_", 
    deparse(substitute(plot_data_structure_data))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/AnalysisData/value_labels_", 
    deparse(substitute(plot_data_structure_data))), ".yml"))

@@

Figure \@ref(fig:ReliabilityReportingFlowDiagram) depicts the flow of measures in relation to reliability reporting. First, it shows that almost half of the measures in both replication (n = `r apa_num(table(coded_data_replications$N_items)["1 item measure"])`) and original research (n = `r apa_num(table(coded_data_original_shortened$N_items)["1 item measure"])`) were single-item measures. When looking at the multiple item measures, the graph illustrates that `r N_reported_reliabilities_replications` measures in the replication protocols and `r N_reported_reliabilities_original` in the original articles reported a reliability coefficient. The most commonly reported reliability coefficient was Cronbach's Alpha, which accounted for `r apa_num(sum(table(coded_data_replications$N_items, coded_data_replications$reliability_type)["multiple item measure", "alpha"]), numerals = FALSE)` reported reliabilities in the replication protocols, and `r apa_num(sum(table(coded_data_original_shortened$N_items, coded_data_original_shortened$reliability_type)["multiple item measure", "alpha"]))` in the original articles.

@@

>>>>

author: 
  - name          : "Goos, C."
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Professor Cobbenhagenlaan 125, 5037 DB, Tilburg, The Netherlands"
    email         : "c.goos@tilburguniversity.edu"
    role: # Contributorship roles (e.g., CRediT, https://credit.niso.org/)
      - "Conceptualization"
      - "Data curation"
      - "Formal Analysis"
      - "Investigation"
      - "Methodology"
      - "Project Administration"
      - "Software"
      - "Visualization"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"
  - name          : "Bakker, M."
    affiliation   : "1"
    role:
      - "Conceptualization"
      - "Supervision"
      - "Writing - Review & Editing"
  - name          : "Wicherts, J.M."
    affiliation   : "1"
    role:
      - "Conceptualization"
      - "Supervision"
      - "Writing - Review & Editing"
  - name          : "Nuijten, M.B."
    affiliation   : "1"
    role:
      - "Conceptualization"
      - "Project Administration"
      - "Supervision"
      - "Validation"
      - "Writing - Review & Editing"

@@

To be included in the planned analyses on calculated reliabilities, the measure had to be a scale consisting of multiple items. If cleaned data was available this was chosen over raw data, to ensure that variables were coded as intended (e.g. no reverse-coded items). Pilot data were omitted from the analyses entirely. These criteria resulted in suitable item score data from `r apa_num(nrow(data_h3_avg))` replication sets spread across on average approximately `r apa_num(mean(table(data_h3_multiple$g)), digits = 0)` lab locations for the analyses of Hypotheses 2 & 3.

@@

## graphs
# plot accompanying the results for Hypotheses 4, 5, & 6.
plot_456_data <- data_prep_plot_456(data_h6)
# plot accompanying the results for Hypotheses 4, & 6
plot_46_data <- data_prep_plot_46(data_h6[c(3, 6, 9, 12, 15, 18, 36, 39, 42, 45, 48, 51)])
plot_46_data_rev <- data_prep_plot_46(data_h6[c(3, 21, 24, 27, 30, 33, 36, 54, 57, 60, 63, 66)])
# plot accompanying the results for Hypotheses 2, & 3
plot_23_data_alpha <- data_prep_plot_23_alpha(data_h3_multiple)
plot_23_data_omega <- data_prep_plot_23_omega(data_h3_multiple)
plot_23_data_reported_alpha <- data_prep_plot_23_alpha_reported(coded_data_original_shortened, data_h3_avg, data_h3_multiple)

@@

@@

Figure \@ref(fig:ReliabilityReportingFlowDiagram) depicts the flow of measures in relation to reliability reporting. First, it shows that almost half of the measures in both replication (n = `r apa_num(sum(coded_data_replications$N_items == "1 item measure"))`) and original research (n = `r apa_num(sum(coded_data_original_shortened$N_items == "1 item measure"))`) were single-item measures. When looking at the multiple item measures, the graph illustrates that `r N_reported_reliabilities_replications` measures in the replication protocols and `r N_reported_reliabilities_original` in the original articles reported a reliability coefficient. The most commonly reported reliability coefficient was Cronbach's Alpha, which accounted for `r apa_num(sum(coded_data_replications$reliability_type == "alpha"), numerals = FALSE)` reported reliabilities in the replication protocols, and `r apa_num(sum(coded_data_original_shortened$reliability_type == "alpha"))` in the original articles.

@@

## ORCID iDs
Cas Goos https://orcid.org/0009-0005-3792-4148
Marjan Bakker https://orcid.org/0000-0001-9024-337X
Jelte M. Wicherts https://orcid.org/0000-0003-2415-2933
Michèle B. Nuijten https://orcid.org/0000-0002-1468-8585

## Funding
The preparation of this article was supported by the veni grant ??? awarded to Michèle Nuijten, and the vici grant ???  awarded to Jelte M. Wicherts from the Netherlands Organization for Scientific Research (NWO).
